---
title: "chanwer Showcase"
subtitle: "Every palette, scale, header treatment, surface, chart form and table pattern in the chanwer R package — static (ggplot2, gt) and interactive (highcharter, reactable) — in one HTML document."
author: "Alejandro Abraham"
date: today
lang: en
topic: "Design System"
subject: "chanwer v2.3 / static + interactive"
brand: _extensions/chanwe-brand/brand.yml
format:
  chanwe-brand-html:
    toc: true
    toc-depth: 2
    number-sections: true
    code-fold: true
    code-summary: "Code"
execute:
  echo: true
  warning: false
  message: false
knitr:
  opts_chunk:
    dev: ragg_png
    fig.width: 8.4
    fig.height: 4.6
    dpi: 200
    out.width: "100%"
---

```{r}
#| label: setup
#| include: false
devtools::load_all(".", quiet = TRUE)
chanwe_load_fonts()
knitr::opts_chunk$set(dev = "ragg_png")

library(ggplot2)
library(dplyr)

set.seed(42)

# ── data ────────────────────────────────────────────────────────────────────
mt <- tibble::as_tibble(mtcars, rownames = "model") |>
    mutate(
        cyl = factor(cyl),
        gear = factor(gear),
        am = factor(am, labels = c("Automatic", "Manual")),
        hp_band = cut(
            hp,
            breaks = c(-Inf, 110, 180, Inf),
            labels = c("Low", "Mid", "High")
        )
    )

econ <- economics |>
    filter(date >= as.Date("2000-01-01")) |>
    mutate(unemp_pct = unemploy / pop * 100)

deltas <- tibble::tibble(
    metric = c(
        "Revenue",
        "Gross margin",
        "EBITDA",
        "Opex",
        "Net income",
        "Churn"
    ),
    actual = c(1240.5, 682.1, 310.2, -420.3, 185.7, 42.0),
    qoq = c(12.4, 4.2, -3.1, -1.9, 5.8, -0.8),
    yoy = c(28.1, 9.6, 11.2, 6.3, -2.4, -4.1)
)

months <- seq(as.Date("2025-09-01"), by = "month", length.out = 12)
rev_df <- expand.grid(
    month = months,
    segment = c("Retail", "Wholesale", "Online"),
    stringsAsFactors = FALSE
) |>
    arrange(segment, month) |>
    group_by(segment) |>
    mutate(
        revenue = round(
            c(Retail = 18, Wholesale = 12, Online = 7)[segment] +
                cumsum(rnorm(12, 0.6, 1.1)),
            2
        )
    ) |>
    ungroup()
spread_labels <- function(y, gap) {
    o <- order(y)
    ys <- y[o]
    for (i in seq_along(ys)[-1]) {
        if (ys[i] - ys[i - 1] < gap) ys[i] <- ys[i - 1] + gap
    }
    y[o] <- ys
    y
}
rev_last <- rev_df |>
    group_by(segment) |>
    slice_max(month, n = 1) |>
    ungroup() |>
    mutate(y_lab = spread_labels(revenue, 1.5))

cyl_summary <- mt |>
    group_by(cyl) |>
    summarise(
        avg_mpg = mean(mpg),
        avg_hp = mean(hp),
        avg_wt = mean(wt),
        sd_mpg = sd(mpg),
        n = n(),
        .groups = "drop"
    )

region_rev <- tibble::tibble(
    region = c("North", "Center", "West", "South", "Total"),
    q1 = c(412.1, 388.4, 251.9, 188.1, 1240.5),
    q2 = c(438.0, 371.2, 266.3, 201.5, 1277.0),
    delta = c(6.3, -4.4, 5.7, 7.1, 2.9)
)

heat <- expand.grid(week = 1:12, region = c("North", "Center", "West", "South"))
heat$delta <- round(
    rnorm(nrow(heat), 0, 2) + rep(c(1.4, 0.3, -0.6, -1.5), each = 12),
    1
)
heat_m <- max(abs(heat$delta))

fleet <- mt |>
    select(model, mpg, hp, wt, cyl) |>
    slice_head(n = 8) |>
    mutate(delta = round(rnorm(8, 0, 6), 1))

# ── reusable pieces ──────────────────────────────────────────────────────────
chart <- chanwe_palette("chart")
MONO <- "'JetBrains Mono', ui-monospace, monospace"

kpi_reserves <- chanwe_kpi(
    num = "45,91",
    label = "USD MM",
    period = "05·MAY·2026",
    mtc1_num = "0,19%",
    mtc1_label = "WoW",
    mtc1_direction = "+",
    mtc2_num = "3,17%",
    mtc2_label = "MoM",
    mtc2_direction = "-",
    mtc3_num = "17,78%",
    mtc3_label = "YoY",
    mtc3_direction = "+"
)

p_fleet <- ggplot(mt, aes(wt, mpg, color = hp_band)) +
    geom_point(size = 2.2, alpha = 0.88) +
    geom_smooth(method = "lm", formula = y ~ x, se = FALSE, linewidth = 0.7) +
    scale_color_chanwe_d() +
    labs(
        x = "Weight (1000 lbs)",
        y = "Miles per gallon",
        color = "HP band",
        caption = chanwe_caption("Source: Motor Trend, 1974")
    )

fmt_pct <- function(x) sprintf("%+.1f%%", x)
```

::: {.callout-note}
## How this document is organised
Sections 1–6 are the **static** system (ggplot2 via `theme_chanwe()`), rendered as PNG. Sections 7–9 are the **HTML-native** counterparts: `chanwe_gt()` for static tables, `chanwe_highchart()` for interactive charts, `chanwe_reactable()` for interactive tables — all sharing the same header grammar (eyebrow / title / subtitle / `//` caption) and signed tokens. Every chunk's code is folded under **Code**. The PDF-only patterns (`chanwe_kbl()`, zone highlights, inset figures) live in `chanwer-showcase-pdf.qmd`.
:::

# The Color System

Every color is a named token. `chanwe_palette()` returns the full inventory;
`chanwe_palette("<group>")` one group; `chanwe_preview_palette("<group>")`
draws its swatch grid. Coral is the house lead, blue is structural, green
is positive, vermillion is alert, ink is the neutral anchor.

## The categorical eight

```{r}
#| label: preview-chart
#| fig-height: 3.4
chanwe_preview_palette("chart")
```

## The signed trio

```{r}
#| label: preview-signed
#| fig-height: 2.4
chanwe_preview_palette("signed")
```

## Semantic roles and family ramps

```{r}
#| label: preview-semantic
#| fig-height: 3.4
chanwe_preview_palette("semantic")
```

```{r}
#| label: preview-teal
#| fig-height: 2.4
chanwe_preview_palette("p15_teal")
```

```{r}
#| label: preview-mb
#| fig-height: 3.4
chanwe_preview_palette("mb_orange")
```

# Scales

## Categorical

```{r}
#| label: cat-scatter
ggplot(mt, aes(wt, mpg, color = am)) +
    geom_point(size = 2.6, alpha = 0.9) +
    scale_color_chanwe_d() +
    labs(
        title = chanwe_title(
            "Fuel economy by weight",
            eyebrow = "CATEGORICAL - 2 SERIES"
        ),
        subtitle = chanwe_subtitle(
            "Nominal series only - scatter charts stay at three or fewer"
        ),
        x = "Weight (1000 lbs)",
        y = "MPG",
        color = "Transmission",
        caption = chanwe_caption("Source: mtcars")
    ) +
    theme_chanwe()
```

::: {.callout-warning}
## Series cap
Scatter, bubble and maps: three series maximum — any two marks can sit side by side, so the palette must pass the stricter all-pairs check. Bars, lines and stacks may use up to six.
:::

```{r}
#| label: cat-bars
mpg_drv <- ggplot2::mpg |>
    mutate(
        drv = factor(
            drv,
            levels = c("f", "4", "r"),
            labels = c("Front", "4WD", "Rear")
        ),
        class = reorder(class, class, FUN = length)
    )
ggplot(mpg_drv, aes(y = class, fill = drv)) +
    geom_bar(width = 0.62) +
    scale_fill_chanwe_d() +
    labs(
        title = chanwe_title(
            "Vehicles by class and drivetrain",
            eyebrow = "CATEGORICAL - STACKED BARS"
        ),
        subtitle = chanwe_subtitle(
            "Color encodes a second nominal variable - bars and stacks may use up to six series"
        ),
        x = "Vehicles",
        y = NULL,
        fill = "Drivetrain",
        caption = chanwe_caption("Source: ggplot2::mpg")
    ) +
    theme_chanwe()
```

## Ordinal: one-hue ramp

```{r}
#| label: ordinal
ggplot(mt, aes(hp_band, fill = hp_band)) +
    geom_bar(width = 0.55) +
    scale_fill_chanwe_d(palette = "p15_blue", reverse = TRUE) +
    labs(
        title = chanwe_title(
            "Fleet by horsepower band",
            eyebrow = "ORDINAL - ONE HUE"
        ),
        subtitle = chanwe_subtitle(
            "Low to High reads light to dark in a single family"
        ),
        x = NULL,
        y = "Vehicles",
        caption = chanwe_caption("Source: mtcars")
    ) +
    theme_chanwe(legend_position = "none")
```

## Sequential

```{r}
#| label: seq-teal
ggplot(mt, aes(wt, mpg, color = disp)) +
    geom_point(size = 2.8) +
    scale_color_chanwe_c(palette = "teal") +
    labs(
        title = chanwe_title(
            "Displacement gradient",
            eyebrow = "SEQUENTIAL - TEAL"
        ),
        subtitle = chanwe_subtitle("One hue, light to dark, magnitude only"),
        x = "Weight (1000 lbs)",
        y = "MPG",
        color = "Disp.",
        caption = chanwe_caption("Source: mtcars")
    ) +
    theme_chanwe()
```

```{r}
#| label: seq-orange
ggplot(econ, aes(date, unemp_pct, color = psavert)) +
    geom_line(linewidth = 0.9) +
    scale_color_chanwe_c() +
    labs(
        title = chanwe_title(
            "Unemployment, colored by savings rate",
            eyebrow = "SEQUENTIAL - ORANGE (DEFAULT)"
        ),
        subtitle = chanwe_subtitle(
            "The default gradient anchors on the report primary"
        ),
        x = NULL,
        y = "Unemployment (%)",
        color = "Savings %",
        caption = chanwe_caption("Source: ggplot2::economics")
    ) +
    theme_chanwe()
```

## Diverging

```{r}
#| label: div-heat
#| fig-height: 4.0
ggplot(heat, aes(week, region, fill = delta)) +
    geom_tile(
        color = chanwe_palette("core")[["brand-white"]],
        linewidth = 1.2
    ) +
    scale_fill_chanwe_div(limits = c(-heat_m, heat_m)) +
    scale_x_continuous(breaks = seq(2, 12, by = 2)) +
    labs(
        title = chanwe_title(
            "Weekly delta vs plan",
            eyebrow = "DIVERGING - HEATMAP"
        ),
        subtitle = chanwe_subtitle(
            "Symmetric limits pin zero to the neutral midpoint"
        ),
        x = "Week",
        y = NULL,
        fill = "Δ pp",
        caption = chanwe_caption("Source: simulated")
    ) +
    theme_chanwe()
```

```{r}
#| label: div-heat-cvd
#| fig-height: 4.0
ggplot(heat, aes(week, region, fill = delta)) +
    geom_tile(
        color = chanwe_palette("core")[["brand-white"]],
        linewidth = 1.2
    ) +
    scale_fill_chanwe_div(limits = c(-heat_m, heat_m), cvd = TRUE) +
    scale_x_continuous(breaks = seq(2, 12, by = 2)) +
    labs(
        title = chanwe_title(
            "Weekly delta vs plan, CVD-safe",
            eyebrow = "DIVERGING - CVD = TRUE"
        ),
        subtitle = chanwe_subtitle(
            "Positive arm switches to structural blue; polarity survives deuteranopia"
        ),
        x = "Week",
        y = NULL,
        fill = "Δ pp",
        caption = chanwe_caption("Source: simulated")
    ) +
    theme_chanwe()
```

```{r}
#| label: div-bars
#| fig-height: 5.2
mk <- ggplot2::mpg |>
    group_by(manufacturer) |>
    summarise(hwy = mean(hwy), .groups = "drop") |>
    mutate(delta = hwy - mean(hwy), manufacturer = reorder(manufacturer, delta))
md <- max(abs(mk$delta))
ggplot(mk, aes(delta, manufacturer, fill = delta)) +
    geom_col(width = 0.62) +
    scale_fill_chanwe_div(limits = c(-md, md)) +
    labs(
        title = chanwe_title(
            "Highway MPG vs fleet average",
            eyebrow = "DIVERGING - BARS"
        ),
        subtitle = chanwe_subtitle(
            "Above average in green, below in vermillion"
        ),
        x = "Δ MPG",
        y = NULL,
        caption = chanwe_caption("Source: ggplot2::mpg")
    ) +
    theme_chanwe(legend_position = "none")
```

# The Signed System

One pair everywhere: `chanwe_palette("signed")` drives KPI arrows, table
deltas and the diverging poles. `direction` states the movement (▲/▼);
`valence` states whether that movement is good news and drives the color.

## KPI scoreboard with valence

```{r}
#| label: kpi-valence
#| fig-height: 5.0
ggplot(econ, aes(date, unemp_pct)) +
    geom_line(linewidth = 0.8, color = chart[["chart-blue"]]) +
    labs(
        title = chanwe_title(
            "Unemployment rate",
            eyebrow = "SIGNED - KPI SCOREBOARD"
        ),
        subtitle = chanwe_subtitle(
            "Share of population, monthly",
            kpi = chanwe_kpi(
                num = "3,9",
                label = "PCT",
                period = "APR·2015",
                mtc1_num = "0,1pp",
                mtc1_label = "MoM",
                mtc1_direction = "-",
                mtc1_valence = "good",
                mtc2_num = "0,4pp",
                mtc2_label = "QoQ",
                mtc2_direction = "-",
                mtc2_valence = "good",
                mtc3_num = "1,1pp",
                mtc3_label = "YoY",
                mtc3_direction = "+",
                mtc3_valence = "bad"
            )
        ),
        x = NULL,
        y = "%",
        caption = chanwe_caption("Source: ggplot2::economics")
    ) +
    theme_chanwe()
```

## Signed deltas in an HTML table

`chanwe_gt(signed = )` colours by valence; `smaller_is_better = TRUE`
flips the mapping for cost-like metrics. Here Opex and Churn are split out
so each block carries the right valence.

```{r}
#| label: gt-signed
bigger <- deltas |> filter(!metric %in% c("Opex", "Churn"))
smaller <- deltas |> filter(metric %in% c("Opex", "Churn"))
fmt_deltas <- function(g) {
    g |>
        gt::cols_label(actual = "USD K", qoq = "QoQ", yoy = "YoY") |>
        gt::fmt_number(columns = actual, decimals = 1) |>
        gt::fmt(columns = c(qoq, yoy), fns = fmt_pct)
}
chanwe_gt(
    bigger,
    title = "Quarterly performance — bigger is better",
    eyebrow = "SIGNED - TABLES",
    subtitle = "Positive deltas green, negative vermillion.",
    caption = "Source: finance close, Q1 - simulated",
    stub = "metric",
    signed = c("qoq", "yoy")
) |>
    fmt_deltas()
```

```{r}
#| label: gt-signed-flip
chanwe_gt(
    smaller,
    title = "Cost and churn — smaller is better",
    eyebrow = "SIGNED - TABLES · SMALLER_IS_BETTER = TRUE",
    subtitle = "The same deltas read with flipped valence: a falling cost is green.",
    caption = "Source: finance close, Q1 - simulated",
    stub = "metric",
    signed = c("qoq", "yoy"),
    smaller_is_better = TRUE
) |>
    fmt_deltas()
```

# Header Treatments

The header grammar: mono-caps eyebrow with an orange rule, Archivo title at
1.85× base, Satoshi subtitle, optional note line or KPI scoreboard, and a
`//` source caption.

## Eyebrow · title · subtitle (default)

```{r}
#| label: hdr-default
p_fleet +
    labs(
        title = chanwe_title("Simple fleet view", eyebrow = "HEADER - DEFAULT"),
        subtitle = chanwe_subtitle(
            "Eyebrow, title and subtitle with the header rule"
        )
    ) +
    theme_chanwe()
```

## Subtitle with a note line

```{r}
#| label: hdr-note
p_fleet +
    labs(
        title = chanwe_title(
            "Transmission comparison",
            eyebrow = "HEADER - NOTE LINE"
        ),
        subtitle = chanwe_subtitle(
            "Linear fit per horsepower band",
            note = "Excludes exotics; n = 32; OLS with no interaction terms"
        )
    ) +
    theme_chanwe()
```

## KPI scoreboard

```{r}
#| label: hdr-kpi
#| fig-height: 5.4
p_fleet +
    labs(
        title = chanwe_title(
            "Reservas Internacionales",
            eyebrow = "BCRA · SECTOR EXTERNO"
        ),
        subtitle = chanwe_subtitle(
            "Evolución de reservas internacionales brutas (USD MM).",
            kpi = kpi_reserves
        )
    ) +
    theme_chanwe(bg_color = "white", plot_borders = TRUE)
```

## KPI only · no subtitle text

```{r}
#| label: hdr-kpi-only
#| fig-height: 5.2
p_fleet +
    labs(
        title = chanwe_title(
            "KPI only · no subtitle text",
            eyebrow = "KPI · COMPACT"
        ),
        subtitle = chanwe_subtitle("", kpi = kpi_reserves)
    ) +
    theme_chanwe()
```

## Title only · has_subtitle = FALSE

```{r}
#| label: hdr-title-only
#| fig-height: 4.3
p_fleet +
    labs(
        title = chanwe_title(
            "Title only · no subtitle",
            eyebrow = "HEADER - HAS_SUBTITLE = FALSE"
        )
    ) +
    theme_chanwe(has_subtitle = FALSE)
```

## Plain title · no eyebrow

```{r}
#| label: hdr-plain
#| fig-height: 4.3
p_fleet +
    labs(
        title = "Plain title, no eyebrow",
        subtitle = chanwe_subtitle(
            "A plain string works when no eyebrow is needed"
        )
    ) +
    theme_chanwe()
```

## No title · no subtitle

```{r}
#| label: hdr-none
#| fig-height: 4.0
p_fleet + theme_chanwe()
```

## Header line and spacing

::: {layout-ncol=2}

```{r}
#| label: hdr-line-spacious
p_fleet +
    labs(
        title = chanwe_title(
            "With subtitle · spacious · no line",
            eyebrow = "HEADER LINE · FALSE"
        ),
        subtitle = chanwe_subtitle(
            "compact_title = FALSE  ·  header_line = FALSE"
        )
    ) +
    theme_chanwe(compact_title = FALSE, header_line = FALSE)
```

```{r}
#| label: hdr-line-compact
p_fleet +
    labs(
        title = chanwe_title(
            "With subtitle · compact · no line",
            eyebrow = "HEADER LINE · FALSE"
        ),
        subtitle = chanwe_subtitle(
            "compact_title = TRUE  ·  header_line = FALSE"
        )
    ) +
    theme_chanwe(compact_title = TRUE, header_line = FALSE)
```

```{r}
#| label: hdr-line-nosub-spacious
p_fleet +
    labs(
        title = chanwe_title(
            "No subtitle · spacious · no line",
            eyebrow = "HEADER LINE · FALSE"
        )
    ) +
    theme_chanwe(
        has_subtitle = FALSE,
        compact_title = FALSE,
        header_line = FALSE
    )
```

```{r}
#| label: hdr-line-nosub-compact
p_fleet +
    labs(
        title = chanwe_title(
            "No subtitle · compact · no line",
            eyebrow = "HEADER LINE · FALSE"
        )
    ) +
    theme_chanwe(
        has_subtitle = FALSE,
        compact_title = TRUE,
        header_line = FALSE
    )
```

:::

```{r}
#| label: hdr-compact-false
p_fleet +
    labs(
        title = chanwe_title(
            "Spacious title",
            eyebrow = "COMPACT_TITLE = FALSE"
        ),
        subtitle = chanwe_subtitle("gap_ln · 14pt  ·  compact_title = FALSE")
    ) +
    theme_chanwe(compact_title = FALSE)
```

# Surfaces and Frames

`theme_chanwe()` exposes five named surfaces plus `"transparent"` and raw
hex; grid colors adapt per surface.

::: {layout-ncol=2}

```{r}
#| label: bg-metallic
p_fleet +
    labs(
        title = chanwe_title("metallic · default", eyebrow = "SURFACE"),
        subtitle = chanwe_subtitle("theme_chanwe()")
    ) +
    theme_chanwe()
```

```{r}
#| label: bg-white
p_fleet +
    labs(
        title = chanwe_title("white", eyebrow = "SURFACE"),
        subtitle = chanwe_subtitle('theme_chanwe(bg_color = "white")')
    ) +
    theme_chanwe(bg_color = "white")
```

```{r}
#| label: bg-ivory
p_fleet +
    labs(
        title = chanwe_title("white-ivory", eyebrow = "SURFACE"),
        subtitle = chanwe_subtitle('theme_chanwe(bg_color = "white-ivory")')
    ) +
    theme_chanwe(bg_color = "white-ivory")
```

```{r}
#| label: bg-gray
p_fleet +
    labs(
        title = chanwe_title("gray", eyebrow = "SURFACE"),
        subtitle = chanwe_subtitle('theme_chanwe(bg_color = "gray")')
    ) +
    theme_chanwe(bg_color = "gray")
```

```{r}
#| label: bg-beige
p_fleet +
    labs(
        title = chanwe_title("beige · padding 18", eyebrow = "SURFACE"),
        subtitle = chanwe_subtitle(
            'theme_chanwe(bg_color = "beige", plot_padding = 18)'
        )
    ) +
    theme_chanwe(bg_color = "beige", plot_padding = 18)
```

```{r}
#| label: bg-transparent
#| dev.args: !expr list(bg = "transparent")
p_fleet +
    labs(
        title = chanwe_title("transparent", eyebrow = "SURFACE"),
        subtitle = chanwe_subtitle(
            'theme_chanwe(bg_color = "transparent") - the page shows through'
        )
    ) +
    theme_chanwe(bg_color = "transparent")
```

:::

## Frames

::: {layout-ncol=2}

```{r}
#| label: frame-true
p_fleet +
    labs(
        title = chanwe_title("plot_borders · TRUE", eyebrow = "FRAME"),
        subtitle = chanwe_subtitle("Thin ink frame lines on the white surface")
    ) +
    theme_chanwe(bg_color = "white", plot_borders = TRUE)
```

```{r}
#| label: frame-top-bottom
ggplot(mt, aes(wt, mpg)) +
    geom_point(size = 2.2, color = chart[["chart-teal"]]) +
    labs(
        title = chanwe_title("plot_borders · top_bottom", eyebrow = "FRAME"),
        subtitle = chanwe_subtitle('plot_borders = "top_bottom"'),
        x = "Weight",
        y = "MPG",
        caption = chanwe_caption("Source: mtcars")
    ) +
    theme_chanwe(plot_borders = "top_bottom")
```

:::

# Chart Forms

## Line · direct labels

```{r}
#| label: form-line
ggplot(rev_df, aes(month, revenue, color = segment)) +
    geom_line(linewidth = 0.8) +
    geom_point(data = rev_last, size = 1.9) +
    geom_text(
        data = rev_last,
        aes(y = y_lab, label = segment),
        hjust = 0,
        nudge_x = 7,
        family = "JetBrains Mono",
        size = 6.75 * 0.72 / ggplot2::.pt,
        show.legend = FALSE
    ) +
    scale_color_chanwe_d() +
    scale_x_date(
        date_labels = "%b",
        breaks = months[c(2, 5, 8, 11)],
        expand = expansion(mult = c(0.02, 0.2))
    ) +
    coord_cartesian(clip = "off") +
    labs(
        title = chanwe_title(
            "Monthly revenue by segment",
            eyebrow = "FORM - LINE"
        ),
        subtitle = chanwe_subtitle(
            "Twelve trailing months, USD MM - series labelled where they end"
        ),
        x = NULL,
        y = "USD MM",
        caption = chanwe_caption("Source: internal ledger, simulated")
    ) +
    theme_chanwe(legend_position = "none")
```

## Area

```{r}
#| label: form-area
ggplot(econ, aes(date, unemploy / 1000)) +
    geom_area(fill = chart[["chart-coral"]], alpha = 0.85) +
    labs(
        title = chanwe_title("Unemployed persons", eyebrow = "FORM - AREA"),
        subtitle = chanwe_subtitle("Millions, monthly since 2000"),
        x = NULL,
        y = "Millions",
        caption = chanwe_caption("Source: ggplot2::economics")
    ) +
    theme_chanwe()
```

## Distribution · density

```{r}
#| label: form-density
ggplot(mt, aes(mpg, fill = am)) +
    geom_density(alpha = 0.7, color = NA) +
    scale_fill_chanwe_d() +
    labs(
        title = chanwe_title(
            "Fuel economy distribution",
            eyebrow = "FORM - DENSITY"
        ),
        subtitle = chanwe_subtitle("Manual transmissions skew to higher MPG"),
        x = "MPG",
        y = "Density",
        fill = NULL,
        caption = chanwe_caption("Source: mtcars")
    ) +
    theme_chanwe()
```

## Error bars · mean ± SD

```{r}
#| label: form-errorbar
ggplot(cyl_summary, aes(cyl, avg_mpg)) +
    geom_pointrange(
        aes(ymin = avg_mpg - sd_mpg, ymax = avg_mpg + sd_mpg),
        color = chart[["chart-blue"]],
        linewidth = 0.7,
        size = 0.6
    ) +
    labs(
        title = chanwe_title(
            "Fuel economy by cylinders",
            eyebrow = "FORM - ERROR BARS"
        ),
        subtitle = chanwe_subtitle("Mean ± one standard deviation"),
        x = "Cylinders",
        y = "MPG",
        caption = chanwe_caption("Source: mtcars")
    ) +
    theme_chanwe()
```

## Focus bar · value labels

```{r}
#| label: form-focus
ggplot(cyl_summary, aes(cyl, avg_mpg)) +
    geom_col(aes(fill = cyl == "4"), width = 0.62) +
    geom_text(
        aes(label = sprintf("%.1f", avg_mpg)),
        vjust = -0.7,
        family = "JetBrains Mono",
        colour = chanwe_palette("semantic")[["secondary"]],
        size = 6.75 * 0.8 / ggplot2::.pt
    ) +
    scale_fill_manual(
        values = c(
            `TRUE` = chanwe_palette("semantic")[["primary"]],
            `FALSE` = "#D4D4D4"
        ),
        guide = "none"
    ) +
    scale_y_continuous(expand = expansion(mult = c(0, 0.14))) +
    labs(
        title = chanwe_title(
            "Fuel economy by cylinders",
            eyebrow = "FORM - FOCUS BAR"
        ),
        subtitle = chanwe_subtitle(
            "One accent, gray context, values on the bars"
        ),
        x = "Cylinders",
        caption = chanwe_caption("Source: mtcars")
    ) +
    theme_chanwe() +
    theme(
        panel.grid.major.y = element_blank(),
        axis.text.y = element_blank(),
        axis.title.y = element_blank()
    )
```

## Facets

```{r}
#| label: form-facets
#| fig-height: 5.0
ggplot(mt, aes(wt, mpg, color = cyl)) +
    geom_point(size = 2.0) +
    facet_wrap(~am) +
    scale_color_chanwe_d() +
    labs(
        title = chanwe_title(
            "Faceted by transmission",
            eyebrow = "FORM - FACETS"
        ),
        subtitle = chanwe_subtitle("Strip labels in JetBrains Mono Thin"),
        x = "Weight",
        y = "MPG",
        color = "Cyl",
        caption = chanwe_caption("Source: mtcars")
    ) +
    theme_chanwe()
```

# Static HTML Tables — `chanwe_gt()`

The HTML counterpart of `chanwe_kbl()`: same header grammar, mono-caps
column labels, tabular mono figures, hairline ink rules, 1px stub and
header rules, striped rows, `//` source note. Returns a `gt_tbl`, so every
`gt` verb can be piped after it.

## Surfaces

```{r}
#| label: gt-white
chanwe_gt(
    fleet |> select(-delta),
    title = "bg · white",
    eyebrow = "TABLE · SPACIOUS · WHITE",
    subtitle = "density · spacious",
    caption = "Source · Motor Trend, 1974 · mtcars dataset.",
    stub = "model"
) |>
    gt::cols_label(mpg = "MPG", hp = "HP", wt = "Weight", cyl = "Cyl") |>
    gt::fmt_number(columns = c(mpg, wt), decimals = 2) |>
    gt::cols_align("right", columns = cyl)
```

```{r}
#| label: gt-ivory-compact
chanwe_gt(
    fleet |> select(-delta),
    title = "bg · white-ivory",
    eyebrow = "TABLE · COMPACT · WHITE-IVORY",
    subtitle = "density · compact",
    caption = "Source · Motor Trend, 1974 · mtcars dataset.",
    stub = "model",
    density = "compact",
    bg = "white-ivory"
) |>
    gt::cols_label(mpg = "MPG", hp = "HP", wt = "Weight", cyl = "Cyl") |>
    gt::fmt_number(columns = c(mpg, wt), decimals = 2) |>
    gt::cols_align("right", columns = cyl)
```

::: {layout-ncol=2}

```{r}
#| label: gt-metallic
chanwe_gt(
    fleet |> select(model, mpg, hp) |> slice_head(n = 5),
    title = "bg · metallic",
    eyebrow = "TABLE · METALLIC",
    stub = "model",
    bg = "metallic"
) |>
    gt::cols_label(mpg = "MPG", hp = "HP") |>
    gt::fmt_number(columns = mpg, decimals = 2)
```

```{r}
#| label: gt-beige
chanwe_gt(
    fleet |> select(model, mpg, hp) |> slice_head(n = 5),
    title = "bg · beige",
    eyebrow = "TABLE · BEIGE",
    stub = "model",
    bg = "beige"
) |>
    gt::cols_label(mpg = "MPG", hp = "HP") |>
    gt::fmt_number(columns = mpg, decimals = 2)
```

```{r}
#| label: gt-gray
chanwe_gt(
    fleet |> select(model, mpg, hp) |> slice_head(n = 5),
    title = "bg · gray",
    eyebrow = "TABLE · GRAY",
    stub = "model",
    bg = "gray"
) |>
    gt::cols_label(mpg = "MPG", hp = "HP") |>
    gt::fmt_number(columns = mpg, decimals = 2)
```

```{r}
#| label: gt-transparent
chanwe_gt(
    fleet |> select(model, mpg, hp) |> slice_head(n = 5),
    title = "bg · transparent",
    eyebrow = "TABLE · TRANSPARENT",
    stub = "model",
    bg = "transparent"
) |>
    gt::cols_label(mpg = "MPG", hp = "HP") |>
    gt::fmt_number(columns = mpg, decimals = 2)
```

:::

## Signed deltas, totals and spanners

```{r}
#| label: gt-signed-fleet
chanwe_gt(
    fleet,
    title = "Fleet overview",
    eyebrow = "TABLE · SIGNED",
    subtitle = "Eight models, mtcars — deltas vs. plan coloured by valence.",
    caption = "Source · Motor Trend, 1974 · mtcars dataset.",
    stub = "model",
    signed = "delta"
) |>
    gt::cols_label(
        mpg = "MPG",
        hp = "HP",
        wt = "Weight",
        cyl = "Cyl",
        delta = "Δ vs plan"
    ) |>
    gt::fmt_number(columns = c(mpg, wt), decimals = 2) |>
    gt::fmt(columns = delta, fns = fmt_pct) |>
    gt::cols_align("right", columns = cyl)
```

```{r}
#| label: gt-totals
chanwe_gt(
    region_rev,
    title = "Revenue by region",
    eyebrow = "TABLE · TOTAL ROW + SPANNER",
    subtitle = "gt verbs pipe after the helper: a spanner over the quarters and an ink rule above the total row.",
    caption = "Source: finance close - simulated",
    stub = "region",
    signed = "delta"
) |>
    gt::cols_label(q1 = "Q1", q2 = "Q2", delta = "QoQ %") |>
    gt::tab_spanner(label = "USD K", columns = c(q1, q2)) |>
    gt::fmt_number(columns = c(q1, q2), decimals = 1) |>
    gt::fmt(columns = delta, fns = fmt_pct) |>
    gt::tab_style(
        style = list(
            gt::cell_text(weight = 600),
            gt::cell_borders(
                sides = "top",
                color = "#0F0F0F",
                weight = gt::px(1)
            )
        ),
        locations = list(
            gt::cells_body(rows = region == "Total"),
            gt::cells_stub(rows = region == "Total")
        )
    )
```

## Row groups

A grouped tibble becomes gt row groups.

```{r}
#| label: gt-groups
mt |>
    select(am, model, mpg, hp, wt) |>
    group_by(am) |>
    slice_head(n = 4) |>
    chanwe_gt(
        title = "Fleet by transmission",
        eyebrow = "TABLE · ROW GROUPS",
        subtitle = "group_by(am) before chanwe_gt() yields one group per transmission.",
        caption = "Source · Motor Trend, 1974 · mtcars dataset.",
        stub = "model"
    ) |>
    gt::cols_label(mpg = "MPG", hp = "HP", wt = "Weight") |>
    gt::fmt_number(columns = c(mpg, wt), decimals = 2)
```

## Header variants

::: {layout-ncol=2}

```{r}
#| label: gt-title-only
chanwe_gt(
    fleet |> select(model, mpg, hp) |> slice_head(n = 5),
    title = "title only · no subtitle",
    eyebrow = "TABLE · COMPACT HERO",
    caption = "Source · Motor Trend, 1974 · mtcars dataset.",
    stub = "model"
) |>
    gt::cols_label(mpg = "MPG", hp = "HP") |>
    gt::fmt_number(columns = mpg, decimals = 2)
```

```{r}
#| label: gt-no-header
chanwe_gt(
    fleet |> select(model, mpg, hp) |> slice_head(n = 5),
    caption = "Source · Motor Trend, 1974 · mtcars dataset.",
    stub = "model"
) |>
    gt::cols_label(mpg = "MPG", hp = "HP") |>
    gt::fmt_number(columns = mpg, decimals = 2)
```

:::

# Interactive Charts — `chanwe_highchart()`

`chanwe_highchart()` applies the header grammar and chart chrome to any
`highcharter` object: Archivo title block, mono axis ticks, no axis lines,
hairline y-grid, ink tooltip, no exporting menu or credits. Pass
`chanwe_palette("chart")` to `hc_colors()` (or let `chanwe_highchart()` do
it) for discrete colour.

## Line with legend

```{r}
#| label: hc-line
highcharter::hchart(
    rev_df,
    "line",
    highcharter::hcaes(x = month, y = revenue, group = segment)
) |>
    highcharter::hc_yAxis(title = list(text = "USD MM")) |>
    chanwe_highchart(
        title = "Monthly revenue by segment",
        eyebrow = "HIGHCHARTS · LINE",
        subtitle = "Twelve trailing months, USD MM · shared tooltip across series",
        caption = "Source: internal ledger, simulated",
        legend = TRUE
    )
```

## Column, one accent + gray context

```{r}
#| label: hc-column
highcharter::highchart() |>
    highcharter::hc_add_series(
        name = "Mean MPG",
        type = "column",
        data = Map(
            function(y, col) list(y = y, color = col),
            cyl_summary$avg_mpg,
            c(chanwe_palette("semantic")[["primary"]], "#D4D4D4", "#D4D4D4")
        ),
        dataLabels = list(
            enabled = TRUE,
            format = "{y:.1f}",
            # Highcharts checks every fontFamily against the document's
            # loaded stylesheets via a `link[href='<fontFamily>']` selector;
            # MONO's single-quoted 'JetBrains Mono' fallback breaks that
            # selector and blanks the whole chart, so double-quote it here
            # instead (harmless CSS, and chanwe_highchart() does the same
            # internally for its own axis/legend/tooltip fonts).
            style = list(
                fontFamily = '"JetBrains Mono", ui-monospace, monospace',
                fontSize = "11px",
                color = "#0F0F0F",
                textOutline = "none"
            )
        ),
        showInLegend = FALSE
    ) |>
    highcharter::hc_xAxis(
        categories = as.character(cyl_summary$cyl),
        title = list(text = "Cylinders")
    ) |>
    highcharter::hc_yAxis(
        title = list(text = "Mean MPG"),
        labels = list(enabled = FALSE)
    ) |>
    chanwe_highchart(
        title = "Fuel economy by cylinders",
        eyebrow = "HIGHCHARTS · COLUMN",
        subtitle = "One accent, gray context",
        caption = "Source: Motor Trend, 1974"
    )
```

# Interactive Tables — `chanwe_reactable()`

Same header grammar as `chanwe_gt()` above the table, `//` caption below;
mono-caps sortable headers, tabular mono figures, ink current page,
brand-orange hover on page buttons, valence-coloured `signed` columns.

## Signed deltas

```{r}
#| label: rt-signed
chanwe_reactable(
    fleet,
    title = "Fleet overview",
    eyebrow = "REACTABLE · SIGNED",
    subtitle = "Eight models, mtcars — sort any column; deltas coloured by valence.",
    caption = "Source · Motor Trend, 1974 · mtcars dataset.",
    signed = "delta",
    defaultPageSize = 6,
    defaultSorted = list(hp = "desc"),
    columns = list(
        model = reactable::colDef(name = "Model", minWidth = 150),
        mpg = reactable::colDef(
            name = "MPG",
            format = reactable::colFormat(digits = 2)
        ),
        hp = reactable::colDef(name = "HP"),
        wt = reactable::colDef(
            name = "Weight",
            format = reactable::colFormat(digits = 2)
        ),
        cyl = reactable::colDef(
            name = "Cyl",
            align = "right",
            style = list(fontFamily = MONO, fontSize = "12px")
        ),
        delta = reactable::colDef(name = "Δ vs plan", cell = fmt_pct)
    )
)
```

## Search, page sizes and a different surface

```{r}
#| label: rt-search
chanwe_reactable(
    mt |> select(model, cyl, hp, mpg, wt, am),
    title = "Full fleet",
    eyebrow = "REACTABLE · SEARCH + PAGE SIZE",
    subtitle = "All 32 vehicles - type to filter, choose a page size.",
    caption = "Source · Motor Trend, 1974 · mtcars dataset.",
    bg = "white-ivory",
    searchable = TRUE,
    showPageSizeOptions = TRUE,
    pageSizeOptions = c(5, 10, 32),
    defaultPageSize = 10,
    columns = list(
        model = reactable::colDef(name = "Model", minWidth = 160),
        cyl = reactable::colDef(
            name = "Cyl",
            align = "right",
            style = list(fontFamily = MONO, fontSize = "12px")
        ),
        hp = reactable::colDef(name = "HP"),
        mpg = reactable::colDef(
            name = "MPG",
            format = reactable::colFormat(digits = 1)
        ),
        wt = reactable::colDef(
            name = "Weight",
            format = reactable::colFormat(digits = 2)
        ),
        am = reactable::colDef(name = "Transmission")
    )
)
```

## Grouped rows with aggregates

```{r}
#| label: rt-groups
chanwe_reactable(
    mt |> select(cyl, model, mpg, hp, wt),
    title = "Fleet by cylinder count",
    eyebrow = "REACTABLE · GROUP BY",
    subtitle = "Expand a group; the group row shows means.",
    caption = "Source · Motor Trend, 1974 · mtcars dataset.",
    groupBy = "cyl",
    defaultPageSize = 12,
    columns = list(
        cyl = reactable::colDef(name = "Cyl"),
        model = reactable::colDef(
            name = "Model",
            aggregate = "count",
            minWidth = 160
        ),
        mpg = reactable::colDef(
            name = "MPG",
            aggregate = "mean",
            format = reactable::colFormat(digits = 1)
        ),
        hp = reactable::colDef(
            name = "HP",
            aggregate = "mean",
            format = reactable::colFormat(digits = 0)
        ),
        wt = reactable::colDef(
            name = "Weight",
            aggregate = "mean",
            format = reactable::colFormat(digits = 2)
        )
    )
)
```

::: {.callout-tip}
## One system
The signed deltas in the reactable and gt tables, the KPI arrows and the diverging heatmap poles are the same three hexes — `chanwe_palette("signed")`. Change them once and every chart, table and report follows.
:::
