---
title: "ChanWe Extension Showcase"
subtitle: "40 examples across ggplot2, highcharter, reactable, and gt"
author: "ChanWe"
brand: _extensions/chanwe-brand/brand.yml
format:
  html:
    toc: true
    number-sections: true
    code-fold: false
    css:
      - inst/quarto/chanwe-reporting.scss
execute:
  echo: false
  warning: false
  message: false
  fig-width: 7.5
  fig-height: 4.5
---

## Setup

```{r}
if (!requireNamespace("chanweThemes", quietly = TRUE)) {
    devtools::load_all(".")
}

library(chanweThemes)
library(ggplot2)
library(dplyr)
library(tidyr)
library(highcharter)
library(reactable)
library(gt)
library(scales)

mt <- tibble::as_tibble(mtcars, rownames = "model")
mt <- mt |>
    mutate(
        cyl = factor(cyl),
        gear = factor(gear),
        am = factor(am, labels = c("Automatic", "Manual"))
    )

mpg2 <- ggplot2::mpg
econ <- ggplot2::economics
iris2 <- iris |>
    mutate(Species = as.character(Species))

mt_summary <- mt |>
    group_by(cyl) |>
    summarise(
        mpg = mean(mpg),
        hp = mean(hp),
        wt = mean(wt),
        qsec = mean(qsec),
        .groups = "drop"
    )
```

Total examples in this document: **40**.

## ggplot2 Examples (1-10)

### Example 1: Scatter by cylinders

```{r}
ggplot(mt, aes(wt, mpg, color = cyl)) +
    geom_point(size = 3, alpha = 0.9) +
    scale_color_chanwe_d() +
    theme_chanwe() +
    labs(title = "MPG vs Weight", subtitle = "Colored by cylinders")
```

### Example 2: Scatter with trend line

```{r}
ggplot(mt, aes(hp, mpg, color = am)) +
    geom_point(size = 2.8) +
    geom_smooth(method = "lm", se = FALSE, linewidth = 0.9) +
    scale_color_chanwe_d() +
    theme_chanwe() +
    labs(title = "Horsepower vs MPG", subtitle = "Linear trend by transmission")
```

### Example 3: Boxplot

```{r}
ggplot(mt, aes(cyl, mpg, fill = cyl)) +
    geom_boxplot(width = 0.65) +
    scale_fill_chanwe_d() +
    theme_chanwe() +
    labs(title = "MPG Distribution", subtitle = "By cylinder group")
```

### Example 4: Violin + jitter

```{r}
ggplot(mt, aes(cyl, qsec, fill = cyl)) +
    geom_violin(alpha = 0.65, color = NA) +
    geom_jitter(width = 0.1, size = 2, color = "#101010") +
    scale_fill_chanwe_d() +
    theme_chanwe() +
    labs(title = "Quarter Mile Time", subtitle = "Violin with observations")
```

### Example 5: Bar chart summary

```{r}
ggplot(mt_summary, aes(cyl, mpg, fill = cyl)) +
    geom_col(width = 0.62) +
    scale_fill_chanwe_d() +
    theme_chanwe() +
    labs(title = "Average MPG", subtitle = "Grouped by cylinders")
```

### Example 6: Line chart over economics time

```{r}
ggplot(econ, aes(date, unemploy / 1000)) +
    geom_line(color = chanwe_palette("chart")[1], linewidth = 0.9) +
    theme_chanwe() +
    labs(
        title = "US Unemployment",
        subtitle = "Economics dataset",
        y = "Thousands"
    )
```

### Example 7: Density chart

```{r}
ggplot(mt, aes(mpg, fill = cyl)) +
    geom_density(alpha = 0.35) +
    scale_fill_chanwe_d() +
    theme_chanwe() +
    labs(title = "Density of MPG", subtitle = "By cylinders")
```

### Example 8: Faceted scatter

```{r}
ggplot(mt, aes(disp, mpg, color = gear)) +
    geom_point(size = 2.5) +
    facet_wrap(~am) +
    scale_color_chanwe_d() +
    theme_chanwe() +
    labs(title = "Displacement vs MPG", subtitle = "Faceted by transmission")
```

### Example 9: Continuous color scale

```{r}
ggplot(mt, aes(wt, mpg, color = hp)) +
    geom_point(size = 3) +
    scale_color_chanwe_c() +
    theme_chanwe() +
    labs(title = "Continuous ChanWe Gradient", subtitle = "HP encoded as color")
```

### Example 10: Area chart

```{r}
series <- econ |>
    select(date, psavert, uempmed) |>
    pivot_longer(-date, names_to = "metric", values_to = "value")

ggplot(series, aes(date, value, fill = metric)) +
    geom_area(position = "stack", alpha = 0.8) +
    scale_fill_chanwe_d() +
    theme_chanwe() +
    labs(title = "Stacked Area", subtitle = "Economic indicators")
```

## highcharter Examples (11-20)

### Example 11: Scatter

```{r}
hchart(mt, "scatter", hcaes(wt, mpg, group = cyl)) |>
    hc_title(text = "Scatter: MPG vs Weight") |>
    hc_add_theme(hc_theme_chanwe())
```

### Example 12: Line

```{r}
hchart(econ |> select(date, unemploy), "line", hcaes(x = date, y = unemploy)) |>
    hc_title(text = "Line: Unemployment over time") |>
    hc_add_theme(hc_theme_chanwe())
```

### Example 13: Column

```{r}
col_df <- mt |>
    count(cyl, name = "n")

hchart(col_df, "column", hcaes(x = cyl, y = n, group = cyl)) |>
    hc_title(text = "Column: Count by cylinders") |>
    hc_add_theme(hc_theme_chanwe())
```

### Example 14: Bar

```{r}
bar_df <- mt |>
    group_by(cyl) |>
    summarise(avg_hp = mean(hp), .groups = "drop")

hchart(bar_df, "bar", hcaes(x = cyl, y = avg_hp, group = cyl)) |>
    hc_title(text = "Bar: Average horsepower") |>
    hc_add_theme(hc_theme_chanwe())
```

### Example 15: Area

```{r}
area_df <- econ |> select(date, psavert)

hchart(area_df, "area", hcaes(x = date, y = psavert)) |>
    hc_title(text = "Area: Personal savings rate") |>
    hc_add_theme(hc_theme_chanwe())
```

### Example 16: Spline

```{r}
spline_df <- mt |>
    arrange(disp) |>
    mutate(idx = row_number())

hchart(spline_df, "spline", hcaes(x = idx, y = mpg, group = cyl)) |>
    hc_title(text = "Spline: Ordered MPG profile") |>
    hc_add_theme(hc_theme_chanwe())
```

### Example 17: Bubble

```{r}
hchart(mt, "bubble", hcaes(wt, mpg, size = hp, group = cyl)) |>
    hc_title(text = "Bubble: HP as size") |>
    hc_add_theme(hc_theme_chanwe())
```

### Example 18: Heatmap

```{r}
num_mat <- mt |>
    select(where(is.numeric)) |>
    cor() |>
    round(2)

hchart(num_mat) |>
    hc_title(text = "Heatmap: Correlation matrix") |>
    hc_add_theme(hc_theme_chanwe())
```

### Example 19: Boxplot

```{r}
hchart(mt, "boxplot", hcaes(x = cyl, y = mpg, group = cyl)) |>
    hc_title(text = "Boxplot: MPG by cylinders") |>
    hc_add_theme(hc_theme_chanwe())
```

### Example 20: Histogram

```{r}
hchart(mt$mpg, name = "MPG") |>
    hc_title(text = "Histogram: MPG distribution") |>
    hc_add_theme(hc_theme_chanwe())
```

## reactable Examples (21-30)

### Example 21: Basic reactable

```{r}
reactable(head(mt, 10), theme = reactable_theme_chanwe())
```

### Example 22: Pagination

```{r}
reactable(mt, theme = reactable_theme_chanwe(), defaultPageSize = 8)
```

### Example 23: Searchable table

```{r}
reactable(mt, theme = reactable_theme_chanwe(), searchable = TRUE)
```

### Example 24: Grouped rows

```{r}
reactable(mt, theme = reactable_theme_chanwe(), groupBy = "cyl")
```

### Example 25: Sorted by MPG descending

```{r}
reactable(
    mt,
    theme = reactable_theme_chanwe(),
    defaultSorted = list(mpg = "desc")
)
```

### Example 26: Highlight horsepower column

```{r}
reactable(
    mt,
    theme = reactable_theme_chanwe(),
    columns = list(
        hp = colDef(
            style = function(value) {
                if (value >= 200) {
                    list(color = "#E94B2B", fontWeight = "700")
                } else {
                    list(color = "#5B5B5B")
                }
            }
        )
    )
)
```

### Example 27: Currency formatting

```{r}
price_df <- mt |>
    transmute(model, cyl, mpg, price_est = mpg * 1250 + hp * 9)

reactable(
    price_df,
    theme = reactable_theme_chanwe(),
    columns = list(
        price_est = colDef(
            format = colFormat(currency = "USD", separators = TRUE)
        )
    )
)
```

### Example 28: Percent formatting

```{r}
share_df <- mt |>
    count(cyl, name = "n") |>
    mutate(share = n / sum(n))

reactable(
    share_df,
    theme = reactable_theme_chanwe(),
    columns = list(
        share = colDef(
            format = colFormat(percent = TRUE, digits = 1)
        )
    )
)
```

### Example 29: Row details

```{r}
reactable(
    mt,
    theme = reactable_theme_chanwe(),
    details = function(index) {
        row <- mt[index, ]
        sprintf(
            "%s | MPG: %.1f | HP: %.0f | Weight: %.2f",
            row$model,
            row$mpg,
            row$hp,
            row$wt
        )
    }
)
```

### Example 30: Single row selection

```{r}
reactable(
    mt,
    theme = reactable_theme_chanwe(),
    selection = "single",
    onClick = "select"
)
```

## gt Examples (31-40)

### Example 31: Basic gt theme

```{r}
gt(head(mt, 10)) |>
    tab_header(title = "GT Basic Table") |>
    gt_theme_chanwe()
```

### Example 32: Number formatting

```{r}
gt(head(mt, 10)) |>
    fmt_number(columns = c(mpg, disp, hp, wt), decimals = 2) |>
    tab_header(title = "Formatted numeric columns") |>
    gt_theme_chanwe()
```

### Example 33: Percent formatting

```{r}
gt(share_df) |>
    fmt_percent(columns = share, decimals = 1) |>
    tab_header(title = "Cylinders share") |>
    gt_theme_chanwe()
```

### Example 34: Currency formatting

```{r}
gt(price_df |> select(model, cyl, price_est)) |>
    fmt_currency(columns = price_est, currency = "USD") |>
    tab_header(title = "Estimated price") |>
    gt_theme_chanwe()
```

### Example 35: Data bars via color scale

```{r}
gt(head(mt, 12)) |>
    data_color(
        columns = mpg,
        method = "numeric",
        palette = chanwe_palette("chart")
    ) |>
    tab_header(title = "MPG color scale") |>
    gt_theme_chanwe()
```

### Example 36: Summary rows

```{r}
gt(mt |> select(cyl, mpg, hp, wt)) |>
    summary_rows(
        groups = TRUE,
        columns = c(mpg, hp, wt),
        fns = list(avg = ~ mean(.), min = ~ min(.), max = ~ max(.))
    ) |>
    tab_header(title = "Grouped summaries") |>
    gt_theme_chanwe()
```

### Example 37: Grand summary row

```{r}
gt(mt |> select(model, mpg, hp, wt)) |>
    grand_summary_rows(
        columns = c(mpg, hp, wt),
        fns = list(total = ~ sum(.), mean = ~ mean(.))
    ) |>
    tab_header(title = "Grand summary") |>
    gt_theme_chanwe()
```

### Example 38: Spanners and labels

```{r}
gt(mt_summary) |>
    cols_label(
        cyl = "Cyl",
        mpg = "Avg MPG",
        hp = "Avg HP",
        wt = "Avg Weight",
        qsec = "Avg 1/4 Mile"
    ) |>
    tab_spanner(label = "Performance", columns = c(mpg, hp, qsec)) |>
    tab_spanner(label = "Vehicle Mass", columns = wt) |>
    tab_header(title = "Spanner layout") |>
    gt_theme_chanwe()
```

### Example 39: Conditional styling

```{r}
gt(head(mt, 15)) |>
    tab_style(
        style = cell_text(weight = "bold", color = "#E94B2B"),
        locations = cells_body(columns = hp, rows = hp >= 200)
    ) |>
    tab_style(
        style = cell_fill(color = "#F8DDD9"),
        locations = cells_body(columns = mpg, rows = mpg < 16)
    ) |>
    tab_header(title = "Conditional styles") |>
    gt_theme_chanwe()
```

### Example 40: Source note and footnote

```{r}
gt(mt_summary) |>
    tab_header(
        title = "ChanWe summary table",
        subtitle = "Example with notes"
    ) |>
    tab_source_note(source_note = md("Source: `mtcars`")) |>
    tab_footnote(
        footnote = "Grouped averages",
        locations = cells_column_labels(columns = mpg)
    ) |>
    gt_theme_chanwe()
```

## Notes

- This document uses your extension via `brand: _extensions/chanwe-brand/brand.yml`.
- HTML is the recommended output for `highcharter` and `reactable` examples.
