---
title: "Chanwe Typst Showcase: ggplot2 + gt"
subtitle: "Simple, complex, compact, and all variants"
author: "Alejandro Abraham"
date: today
keywords: [Quarto, Chanwe, Typst, ggplot2, gt]
bibliography: references.bib
link-citations: true
brand: _extensions/chanwe-brand/brand.yml
format:
  typst:
    toc: true
    number-sections: true
execute:
  echo: false
  warning: false
  message: false
  dev: ragg_png
  fig-format: png
  fig-dpi: 320
---

```{r}
#| label: setup
#| include: false
devtools::load_all(".")

knitr::opts_chunk$set(dev = "ragg_png", dpi = 320)

library(ggplot2)
library(dplyr)
library(tidyr)
library(gt)

mt <- tibble::as_tibble(mtcars, rownames = "model") |>
    mutate(
        cyl = factor(cyl),
        gear = factor(gear),
        am = factor(am, labels = c("Automatic", "Manual")),
        hp_band = cut(
            hp,
            breaks = c(-Inf, 110, 180, Inf),
            labels = c("Low", "Mid", "High")
        )
    )

summary_tbl <- mt |>
    group_by(cyl, am) |>
    summarise(
        avg_mpg = mean(mpg),
        avg_hp = mean(hp),
        avg_wt = mean(wt),
        n = dplyr::n(),
        .groups = "drop"
    )
```

This Typst example focuses on static output quality for both `ggplot2` and
`gt`, including simple and complex examples plus all style variants.

## GGPlot: Simple

```{r}
#| label: fig-simple-scatter-beige
#| fig-cap: "Simple scatter plot (beige background)."
#| fig-width: 7
#| fig-height: 4.2

ggplot(mt, aes(wt, mpg, color = am)) +
    geom_point(size = 2.8, alpha = 0.9) +
    scale_color_chanwe_d() +
    theme_chanwe(background = "beige") +
    labs(
        title = chanwe_title("Fuel economy vs weight"),
        subtitle = chanwe_subtitle("Simple scatter"),
        x = "Weight",
        y = "MPG",
        color = "Transmission",
        caption = 'Fuente: Hadley Wickham'
    )
```

```{r}
#| label: fig-simple-bar-white
#| fig-cap: "Simple bar plot (white background)."
#| fig-width: 7
#| fig-height: 4.2

ggplot(mt, aes(cyl, fill = cyl)) +
    geom_bar(width = 0.65) +
    scale_fill_chanwe_d() +
    theme_chanwe(background = "white") +
    labs(
        title = chanwe_title("Vehicle count by cylinder"),
        subtitle = chanwe_subtitle("Simple bar"),
        x = "Cylinders",
        y = "Count",
        fill = "Cylinders"
    )
```

## GGPlot: Complex

```{r}
#| label: fig-complex-facet
#| fig-cap: "Faceted scatter with regression lines (beige background)."
#| fig-width: 7.4
#| fig-height: 4.8

ggplot(mt, aes(wt, mpg, color = hp_band)) +
    geom_point(size = 2.2, alpha = 0.88) +
    geom_smooth(method = "lm", se = FALSE, linewidth = 0.7) +
    facet_wrap(~am) +
    scale_color_chanwe_d() +
    theme_chanwe(background = "beige") +
    labs(
        title = chanwe_title("Performance profile by transmission"),
        subtitle = chanwe_subtitle("Complex faceted view"),
        x = "Weight",
        y = "MPG",
        color = "HP band"
    )
```

```{r}
#| label: fig-complex-box
#| fig-cap: "Box and jitter overlay by cylinder and transmission (white background)."
#| fig-width: 7.4
#| fig-height: 4.8

ggplot(mt, aes(cyl, mpg, fill = am)) +
    geom_boxplot(alpha = 0.7, outlier.shape = NA, width = 0.62) +
    geom_jitter(width = 0.12, size = 1.8, alpha = 0.75, color = "#101010") +
    scale_fill_chanwe_d() +
    theme_chanwe(background = "white") +
    labs(
        title = chanwe_title("Distribution view"),
        subtitle = chanwe_subtitle("Complex grouped layout"),
        x = "Cylinders",
        y = "MPG",
        fill = "Transmission"
    )
```

## GGPlot: All Variants

```{r}
#| label: fig-all-beige
#| fig-cap: "All variants check: beige background."
#| fig-width: 7
#| fig-height: 4.2

ggplot(mt, aes(hp, mpg, color = cyl)) +
    geom_point(size = 2.4, alpha = 0.9) +
    scale_color_chanwe_d() +
    theme_chanwe(background = "beige") +
    labs(
        title = chanwe_title("Variant check"),
        subtitle = chanwe_subtitle("beige + border #F7F7F7"),
        x = "Horsepower",
        y = "MPG",
        color = "Cylinders"
    )
```

```{r}
#| label: fig-all-white
#| fig-cap: "All variants check: white background."
#| fig-width: 7
#| fig-height: 4.2

ggplot(mt, aes(hp, mpg, color = cyl)) +
    geom_point(size = 2.4, alpha = 0.9) +
    scale_color_chanwe_d() +
    theme_chanwe(background = "white") +
    labs(
        title = chanwe_title("Variant check"),
        subtitle = chanwe_subtitle("white + border #F7F7F7"),
        x = "Horsepower",
        y = "MPG",
        color = "Cylinders"
    )
```

## GT Tables: Simple

```{r}
#| label: tbl-simple
#| tbl-cap: "Simple gt table (white background)."

mt |>
    select(model, mpg, cyl, hp, wt) |>
    slice_head(n = 8) |>
    gt(rowname_col = "model") |>
    gt::fmt_number(columns = c(mpg, hp, wt), decimals = 2) |>
    gt::tab_header(
        title = "Simple fleet view",
        subtitle = "White background"
    ) |>
    gt_theme_chanwe(background = "white")
```

## GT Tables: Compact

```{r}
#| label: tbl-compact
#| tbl-cap: "Compact gt table (beige background)."

mt |>
    select(model, mpg, cyl, gear, am) |>
    slice_head(n = 10) |>
    gt(rowname_col = "model") |>
    gt::tab_header(
        title = "Compact fleet view",
        subtitle = "Beige background"
    ) |>
    gt_theme_chanwe_compact(background = "beige")
```

## GT Tables: Complex

```{r}
#| label: tbl-complex
#| tbl-cap: "Complex gt table with spanners and formatting (white background)."

summary_tbl |>
    gt(groupname_col = "am") |>
    gt::tab_header(
        title = "Complex performance summary",
        subtitle = "Grouped by transmission"
    ) |>
    gt::tab_spanner(label = "Averages", columns = c(avg_mpg, avg_hp, avg_wt)) |>
    gt::cols_label(
        cyl = "Cyl",
        avg_mpg = "MPG",
        avg_hp = "HP",
        avg_wt = "Weight",
        n = "Rows"
    ) |>
    gt::fmt_number(columns = c(avg_mpg, avg_hp, avg_wt), decimals = 2) |>
    gt::fmt_number(columns = n, decimals = 0) |>
    gt::tab_source_note("Source: mtcars aggregated in setup chunk") |>
    gt_theme_chanwe(variant = "spacious", background = "white")
```

## GT Tables: All Variants

```{r}
#| label: tbl-all-spacious-beige
#| tbl-cap: "All variants: spacious + beige."

summary_tbl |>
    gt(groupname_col = "am") |>
    gt::tab_header(title = "Spacious + Beige") |>
    gt::fmt_number(columns = c(avg_mpg, avg_hp, avg_wt), decimals = 2) |>
    gt_theme_chanwe(variant = "spacious", background = "beige")
```

```{r}
#| label: tbl-all-spacious-white
#| tbl-cap: "All variants: spacious + white."

summary_tbl |>
    gt(groupname_col = "am") |>
    gt::tab_header(title = "Spacious + White") |>
    gt::fmt_number(columns = c(avg_mpg, avg_hp, avg_wt), decimals = 2) |>
    gt_theme_chanwe(variant = "spacious", background = "white")
```

```{r}
#| label: tbl-all-compact-beige
#| tbl-cap: "All variants: compact + beige."

summary_tbl |>
    gt(groupname_col = "am") |>
    gt::tab_header(title = "Compact + Beige") |>
    gt::fmt_number(columns = c(avg_mpg, avg_hp, avg_wt), decimals = 2) |>
    gt_theme_chanwe(variant = "compact", background = "beige")
```

```{r}
#| label: tbl-all-compact-white
#| tbl-cap: "All variants: compact + white."

summary_tbl |>
    gt(groupname_col = "am") |>
    gt::tab_header(title = "Compact + White") |>
    gt::fmt_number(columns = c(avg_mpg, avg_hp, avg_wt), decimals = 2) |>
    gt_theme_chanwe(variant = "compact", background = "white")
```

## Notes

- This file is intended for Typst/PDF output.
- It demonstrates simple and complex charts and tables plus all table variants.
- Border intent for both backgrounds is `#F7F7F7`.
