---
title: "Extension & Package Showcase"
subtitle: "40 examples across ggplot2, highcharter, reactable, and gt"
bibliography: references.bib
link-citations: true
author: "Alejandro Abraham"
date: today
topic: "Brand System"
subject: "Quarto Extension"
keywords: [Quarto, Chanwe, ggplot2, highcharter, reactable, gt]
brand: _extensions/chanwe-brand/brand.yml
format:
  html:
    toc: true
    number-sections: true
    code-fold: false
execute:
  echo: false
  warning: false
  message: false
  fig-width: 7.5
  fig-height: 4.5
---

## Quarto Feature Tour {#sec-quarto-tour}

```{r}
#| label: showcase-chunk-01
#| include: false
if (!requireNamespace("chanwer", quietly = TRUE)) {
    devtools::load_all(".")
}

library(chanwer)
library(ggplot2)
library(dplyr)
library(tidyr)
library(highcharter)
library(reactable)
library(gt)
library(scales)

mt <- tibble::as_tibble(mtcars, rownames = "model")
mt <- mt |>
    mutate(
        cyl = factor(cyl),
        gear = factor(gear),
        am = factor(am, labels = c("Automatic", "Manual"))
    )

mpg2 <- ggplot2::mpg
econ <- ggplot2::economics
iris2 <- iris |>
    mutate(Species = as.character(Species))

mt_summary <- mt |>
    group_by(cyl) |>
    summarise(
        mpg = mean(mpg),
        hp = mean(hp),
        wt = mean(wt),
        qsec = mean(qsec),
        .groups = "drop"
    )
```

This document is both a **visual branding showcase** and a **Quarto feature
showcase**. It demonstrates long-form reporting patterns you can reuse in
real client-facing work: callouts, citations, cross-references, columns,
full-width layouts, tables, links, footnotes, tabsets, equations, and rich
content blocks [@allaire2022quarto; @wickham2016ggplot2].

ChanWe styling emphasizes clarity and hierarchy: muted body text, confident
headings, and selective orange accents for high-signal elements. The design
language follows a pragmatic “editorial dashboard” approach rather than a
generic notebook look.^[The objective is readability first, then brand
personality.]

You can jump directly to the examples in [Section @sec-examples], open the
[Quarto docs](https://quarto.org/docs/), or inspect package usage in the
[chanwer README](README.md).

::: {.callout-note title="Document Intent"}
This page intentionally mixes prose and analytical components to mimic a real
report workflow: executive narrative, exploration, and production-ready
visualizations.
:::

::: {.callout-important title="Brand Behavior"}
Use orange as an accent and semantic signal, not as a full-page fill. Dense
orange usage reduces hierarchy and harms scanability.
:::

::: {.callout-warning title="Output Format Guidance"}
`highcharter` and `reactable` are HTML-native widgets. For PDF/PPTX exports,
prefer `ggplot2` and `gt` where static rendering is required.
:::

::: {.aside}
This aside block is useful for constraints, assumptions, or reviewer notes
without interrupting the core narrative.
:::

### Structured Layouts

::: {.columns}
::: {.column width="55%"}
The left column carries narrative context, assumptions, and interpretation.
This is useful for executive summaries where each chart needs a concise
takeaway.

- Keep section intros short and explicit.
- Use callouts for risk/status signals.
- Prefer references to labeled figures and tables over “see above”.
:::
::: {.column width="45%"}
```{r}
#| label: fig-quick-look
#| fig-cap: "Quick look: MPG vs Weight with ChanWe defaults."
ggplot(mt, aes(wt, mpg, color = cyl)) +
    geom_point(size = 3, alpha = 0.9) +
    scale_color_chanwe_d() +
    theme_chanwe() +
    labs(
        title = "Quick Look",
        subtitle = chanwe_subtitle("Performance profile by cylinder")
    )
```

:::
:::

As shown in @fig-quick-look, the subtitle accent line creates a compact visual
anchor between heading text and chart body.

::: {.column-page}
### Full-Width Comparison

Use a wider layout for side-by-side displays where detail density is high.

```{r}
#| label: showcase-chunk-03
#| layout-ncol: 2
ggplot(mt, aes(hp, mpg, color = am)) +
    geom_point(size = 2.6) +
    geom_smooth(method = "lm", se = FALSE, linewidth = 0.8) +
    scale_color_chanwe_d() +
    theme_chanwe() +
    labs(title = "Model View", subtitle = chanwe_subtitle("Regression trend"))

gt(head(mt, 10)) |>
    tab_header(title = "Operational Snapshot") |>
    gt_theme_chanwe()
```

:::

### Cross-Refs, Tables, and Equation

```{r}
#| label: tbl-semantic-tokens
#| tbl-cap: "Core semantic tokens used in this report."
token_tbl <- tibble::tribble(
    ~token       , ~value    , ~usage                      ,
    "foreground" , "#5B5B5B" , "Body text"                 ,
    "background" , "#F7F7F7" , "Page/panel background"     ,
    "primary"    , "#E94B2B" , "Accent and highlights"     ,
    "info"       , "#11F7E6" , "Informational callouts"    ,
    "success"    , "#1EB508" , "Positive status callouts"  ,
    "danger"     , "#F40C0C" , "Risk and caution callouts"
)
knitr::kable(token_tbl, align = c("l", "l", "l"))
```

Table @tbl-semantic-tokens summarizes the semantic mapping used by the theme.

The simplified visual quality score used in this narrative is:

$$
Q = 0.6 \\times R + 0.4 \\times B
$$ {#eq-quality}

where \(R\) is readability and \(B\) is brand consistency. Equation @eq-quality
is illustrative but helps show how math is rendered in the same styled flow.

### Tabs and Rich Content

::: {.panel-tabset}
## Narrative

A good branded report combines:

1. Context and business framing.
2. Visual evidence with consistent semantics.
3. Action-oriented summaries and explicit caveats.

## Technical Notes

```{r}
#| label: showcase-chunk-05
list(
    extension = "_extensions/chanwe-brand/brand.yml",
    report_css = chanwe_reporting_css(),
    chart_palette = unname(chanwe_palette("chart"))
)
```

## Links

- [Quarto Guide](https://quarto.org/docs/)
- [ggplot2 Reference](https://ggplot2.tidyverse.org/)
- [gt Documentation](https://gt.rstudio.com/)
- [reactable Documentation](https://glin.github.io/reactable/)
- [highcharter Documentation](https://jkunst.com/highcharter/)
:::

## Component Examples {#sec-examples}

## Setup

```{r}
#| label: showcase-chunk-06
if (!requireNamespace("chanwer", quietly = TRUE)) {
    devtools::load_all(".")
}

library(chanwer)
library(ggplot2)
library(dplyr)
library(tidyr)
library(highcharter)
library(reactable)
library(gt)
library(scales)

mt <- tibble::as_tibble(mtcars, rownames = "model")
mt <- mt |>
    mutate(
        cyl = factor(cyl),
        gear = factor(gear),
        am = factor(am, labels = c("Automatic", "Manual"))
    )

mpg2 <- ggplot2::mpg
econ <- ggplot2::economics
iris2 <- iris |>
    mutate(Species = as.character(Species))

mt_summary <- mt |>
    group_by(cyl) |>
    summarise(
        mpg = mean(mpg),
        hp = mean(hp),
        wt = mean(wt),
        qsec = mean(qsec),
        .groups = "drop"
    )
```

Total examples in this document: **40**.

## ggplot2 Examples (1-10)

### Example 1: Scatter by cylinders

```{r}
#| label: showcase-chunk-07
ggplot(mt, aes(wt, mpg, color = cyl)) +
    geom_point(size = 3, alpha = 0.9) +
    scale_color_chanwe_d() +
    theme_chanwe() +
    labs(title = "MPG vs Weight", subtitle = "Colored by cylinders")
```

### Example 2: Scatter with trend line

```{r}
#| label: showcase-chunk-08
ggplot(mt, aes(hp, mpg, color = am)) +
    geom_point(size = 2.8) +
    geom_smooth(method = "lm", se = FALSE, linewidth = 0.9) +
    scale_color_chanwe_d() +
    theme_chanwe() +
    labs(title = "Horsepower vs MPG", subtitle = "Linear trend by transmission")
```

### Example 3: Boxplot

```{r}
#| label: showcase-chunk-09
ggplot(mt, aes(cyl, mpg, fill = cyl)) +
    geom_boxplot(width = 0.65) +
    scale_fill_chanwe_d() +
    theme_chanwe() +
    labs(title = "MPG Distribution", subtitle = "By cylinder group")
```

### Example 4: Violin + jitter

```{r}
#| label: showcase-chunk-10
ggplot(mt, aes(cyl, qsec, fill = cyl)) +
    geom_violin(alpha = 0.65, color = NA) +
    geom_jitter(width = 0.1, size = 2, color = "#101010") +
    scale_fill_chanwe_d() +
    theme_chanwe() +
    labs(title = "Quarter Mile Time", subtitle = "Violin with observations")
```

### Example 5: Bar chart summary

```{r}
#| label: showcase-chunk-11
ggplot(mt_summary, aes(cyl, mpg, fill = cyl)) +
    geom_col(width = 0.62) +
    scale_fill_chanwe_d() +
    theme_chanwe() +
    labs(title = "Average MPG", subtitle = "Grouped by cylinders")
```

### Example 6: Line chart over economics time

```{r}
#| label: showcase-chunk-12
ggplot(econ, aes(date, unemploy / 1000)) +
    geom_line(color = chanwe_palette("chart")[1], linewidth = 0.9) +
    theme_chanwe() +
    labs(
        title = "US Unemployment",
        subtitle = "Economics dataset",
        y = "Thousands"
    )
```

### Example 7: Density chart

```{r}
#| label: showcase-chunk-13
ggplot(mt, aes(mpg, fill = cyl)) +
    geom_density(alpha = 0.35) +
    scale_fill_chanwe_d() +
    theme_chanwe() +
    labs(title = "Density of MPG", subtitle = "By cylinders")
```

### Example 8: Faceted scatter

```{r}
#| label: showcase-chunk-14
ggplot(mt, aes(disp, mpg, color = gear)) +
    geom_point(size = 2.5) +
    facet_wrap(~am) +
    scale_color_chanwe_d() +
    theme_chanwe() +
    labs(title = "Displacement vs MPG", subtitle = "Faceted by transmission")
```

### Example 9: Continuous color scale

```{r}
#| label: showcase-chunk-15
ggplot(mt, aes(wt, mpg, color = hp)) +
    geom_point(size = 3) +
    scale_color_chanwe_c() +
    theme_chanwe() +
    labs(title = "Continuous ChanWe Gradient", subtitle = "HP encoded as color")
```

### Example 10: Area chart

```{r}
#| label: showcase-chunk-16
series <- econ |>
    select(date, psavert, uempmed) |>
    pivot_longer(-date, names_to = "metric", values_to = "value")

ggplot(series, aes(date, value, fill = metric)) +
    geom_area(position = "stack", alpha = 0.8) +
    scale_fill_chanwe_d() +
    theme_chanwe() +
    labs(title = "Stacked Area", subtitle = "Economic indicators")
```

## highcharter Examples (11-20)

### Example 11: Scatter

```{r}
#| label: showcase-chunk-17
hchart(mt, "scatter", hcaes(wt, mpg, group = cyl)) |>
    hc_title(text = "Scatter: MPG vs Weight") |>
    hc_add_theme(hc_theme_chanwe())
```

### Example 12: Line

```{r}
#| label: showcase-chunk-18
hchart(econ |> select(date, unemploy), "line", hcaes(x = date, y = unemploy)) |>
    hc_title(text = "Line: Unemployment over time") |>
    hc_add_theme(hc_theme_chanwe())
```

### Example 13: Column

```{r}
#| label: showcase-chunk-19
col_df <- mt |>
    count(cyl, name = "n")

hchart(col_df, "column", hcaes(x = cyl, y = n, group = cyl)) |>
    hc_title(text = "Column: Count by cylinders") |>
    hc_add_theme(hc_theme_chanwe())
```

### Example 14: Bar

```{r}
#| label: showcase-chunk-20
bar_df <- mt |>
    group_by(cyl) |>
    summarise(avg_hp = mean(hp), .groups = "drop")

hchart(bar_df, "bar", hcaes(x = cyl, y = avg_hp, group = cyl)) |>
    hc_title(text = "Bar: Average horsepower") |>
    hc_add_theme(hc_theme_chanwe())
```

### Example 15: Area

```{r}
#| label: showcase-chunk-21
area_df <- econ |> select(date, psavert)

hchart(area_df, "area", hcaes(x = date, y = psavert)) |>
    hc_title(text = "Area: Personal savings rate") |>
    hc_add_theme(hc_theme_chanwe())
```

### Example 16: Spline

```{r}
#| label: showcase-chunk-22
spline_df <- mt |>
    arrange(disp) |>
    mutate(idx = row_number())

hchart(spline_df, "spline", hcaes(x = idx, y = mpg, group = cyl)) |>
    hc_title(text = "Spline: Ordered MPG profile") |>
    hc_add_theme(hc_theme_chanwe())
```

### Example 17: Bubble

```{r}
#| label: showcase-chunk-23
hchart(mt, "bubble", hcaes(wt, mpg, size = hp, group = cyl)) |>
    hc_title(text = "Bubble: HP as size") |>
    hc_add_theme(hc_theme_chanwe())
```

### Example 18: Heatmap

```{r}
#| label: showcase-chunk-24
num_mat <- mt |>
    select(where(is.numeric)) |>
    cor() |>
    round(2)

hchart(num_mat) |>
    hc_title(text = "Heatmap: Correlation matrix") |>
    hc_add_theme(hc_theme_chanwe())
```

### Example 19: Boxplot

```{r}
#| label: showcase-chunk-25
hchart(mt, "boxplot", hcaes(x = cyl, y = mpg, group = cyl)) |>
    hc_title(text = "Boxplot: MPG by cylinders") |>
    hc_add_theme(hc_theme_chanwe())
```

### Example 20: Histogram

```{r}
#| label: showcase-chunk-26
hchart(mt$mpg, name = "MPG") |>
    hc_title(text = "Histogram: MPG distribution") |>
    hc_add_theme(hc_theme_chanwe())
```

## reactable Examples (21-30)

### Example 21: Basic reactable

```{r}
#| label: showcase-chunk-27
reactable(head(mt, 10), theme = reactable_theme_chanwe())
```

### Example 22: Pagination

```{r}
#| label: showcase-chunk-28
reactable(mt, theme = reactable_theme_chanwe(), defaultPageSize = 8)
```

### Example 23: Searchable table

```{r}
#| label: showcase-chunk-29
reactable(mt, theme = reactable_theme_chanwe(), searchable = TRUE)
```

### Example 24: Grouped rows

```{r}
#| label: showcase-chunk-30
reactable(mt, theme = reactable_theme_chanwe(), groupBy = "cyl")
```

### Example 25: Sorted by MPG descending

```{r}
#| label: showcase-chunk-31
reactable(
    mt,
    theme = reactable_theme_chanwe(),
    defaultSorted = list(mpg = "desc")
)
```

### Example 26: Highlight horsepower column

```{r}
#| label: showcase-chunk-32
reactable(
    mt,
    theme = reactable_theme_chanwe(),
    columns = list(
        hp = colDef(
            style = function(value) {
                if (value >= 200) {
                    list(color = "#E94B2B", fontWeight = "700")
                } else {
                    list(color = "#5B5B5B")
                }
            }
        )
    )
)
```

### Example 27: Currency formatting

```{r}
#| label: showcase-chunk-33
price_df <- mt |>
    transmute(model, cyl, mpg, price_est = mpg * 1250 + hp * 9)

reactable(
    price_df,
    theme = reactable_theme_chanwe(),
    columns = list(
        price_est = colDef(
            format = colFormat(currency = "USD", separators = TRUE)
        )
    )
)
```

### Example 28: Percent formatting

```{r}
#| label: showcase-chunk-34
share_df <- mt |>
    count(cyl, name = "n") |>
    mutate(share = n / sum(n))

reactable(
    share_df,
    theme = reactable_theme_chanwe(),
    columns = list(
        share = colDef(
            format = colFormat(percent = TRUE, digits = 1)
        )
    )
)
```

### Example 29: Row details

```{r}
#| label: showcase-chunk-35
reactable(
    mt,
    theme = reactable_theme_chanwe(),
    details = function(index) {
        row <- mt[index, ]
        sprintf(
            "%s | MPG: %.1f | HP: %.0f | Weight: %.2f",
            row$model,
            row$mpg,
            row$hp,
            row$wt
        )
    }
)
```

### Example 30: Single row selection

```{r}
#| label: showcase-chunk-36
reactable(
    mt,
    theme = reactable_theme_chanwe(),
    selection = "single",
    onClick = "select"
)
```

## gt Examples (31-40)

### Example 31: Basic gt theme

```{r}
#| label: showcase-chunk-37
gt(head(mt, 10)) |>
    tab_header(title = "GT Basic Table") |>
    gt_theme_chanwe()
```

### Example 32: Number formatting

```{r}
#| label: showcase-chunk-38
gt(head(mt, 10)) |>
    fmt_number(columns = c(mpg, disp, hp, wt), decimals = 2) |>
    tab_header(title = "Formatted numeric columns") |>
    gt_theme_chanwe()
```

### Example 33: Percent formatting

```{r}
#| label: showcase-chunk-39
gt(share_df) |>
    fmt_percent(columns = share, decimals = 1) |>
    tab_header(title = "Cylinders share") |>
    gt_theme_chanwe()
```

### Example 34: Currency formatting

```{r}
#| label: showcase-chunk-40
gt(price_df |> select(model, cyl, price_est)) |>
    fmt_currency(columns = price_est, currency = "USD") |>
    tab_header(title = "Estimated price") |>
    gt_theme_chanwe()
```

### Example 35: Data bars via color scale

```{r}
#| label: showcase-chunk-41
gt(head(mt, 12)) |>
    data_color(
        columns = mpg,
        method = "numeric",
        palette = chanwe_palette("chart")
    ) |>
    tab_header(title = "MPG color scale") |>
    gt_theme_chanwe()
```

### Example 36: Summary rows

```{r}
#| label: showcase-chunk-42
gt(mt |> select(cyl, mpg, hp, wt)) |>
    summary_rows(
        groups = TRUE,
        columns = c(mpg, hp, wt),
        fns = list(avg = ~ mean(.), min = ~ min(.), max = ~ max(.))
    ) |>
    tab_header(title = "Grouped summaries") |>
    gt_theme_chanwe()
```

### Example 37: Grand summary row

```{r}
#| label: showcase-chunk-43
gt(mt |> select(model, mpg, hp, wt)) |>
    grand_summary_rows(
        columns = c(mpg, hp, wt),
        fns = list(total = ~ sum(.), mean = ~ mean(.))
    ) |>
    tab_header(title = "Grand summary") |>
    gt_theme_chanwe()
```

### Example 38: Spanners and labels

```{r}
#| label: showcase-chunk-44
gt(mt_summary) |>
    cols_label(
        cyl = "Cyl",
        mpg = "Avg MPG",
        hp = "Avg HP",
        wt = "Avg Weight",
        qsec = "Avg 1/4 Mile"
    ) |>
    tab_spanner(label = "Performance", columns = c(mpg, hp, qsec)) |>
    tab_spanner(label = "Vehicle Mass", columns = wt) |>
    tab_header(title = "Spanner layout") |>
    gt_theme_chanwe()
```

### Example 39: Conditional styling

```{r}
#| label: showcase-chunk-45
gt(head(mt, 15)) |>
    tab_style(
        style = cell_text(weight = "bold", color = "#E94B2B"),
        locations = cells_body(columns = hp, rows = hp >= 200)
    ) |>
    tab_style(
        style = cell_fill(color = "#F8DDD9"),
        locations = cells_body(columns = mpg, rows = mpg < 16)
    ) |>
    tab_header(title = "Conditional styles") |>
    gt_theme_chanwe()
```

### Example 40: Source note and footnote

```{r}
#| label: showcase-chunk-46
gt(mt_summary) |>
    tab_header(
        title = "ChanWe summary table",
        subtitle = "Example with notes"
    ) |>
    tab_source_note(source_note = md("Source: `mtcars`")) |>
    tab_footnote(
        footnote = "Grouped averages",
        locations = cells_column_labels(columns = mpg)
    ) |>
    gt_theme_chanwe()
```

## Notes

- This document uses your extension via `brand: _extensions/chanwe-brand/brand.yml`.
- HTML is the recommended output for `highcharter` and `reactable` examples.
- Core Quarto blocks demonstrated: citations, callouts, aside, columns,
  full-width layout, tabsets, links, footnotes, equations, and cross-refs.
