---
title: "Chanwe Showcase: ggplot2 + gt"
subtitle: "Tables and plots styled with chanwe-typst design tokens"
author: "Alejandro Abraham"
date: today
bibliography: references.bib
format:
  chanwe-typst:
    keep-typ: false
    number-sections: true
    section-numbering: 1.1
execute:
  echo: false
  warning: false
  message: false
  dev: ragg_png
  fig-format: png
  fig-dpi: 320
chanwe:
  document: "CHW · DEV"
  edition: "SHOWCASE / 2026"
  cover: false
  toc: true
  toc-title: "Contents"
  back-cover: false
---

```{r}
#| label: setup
#| include: false
devtools::load_all(".")

knitr::opts_chunk$set(dev = "ragg_png", dpi = 320)

library(ggplot2)
library(dplyr)
library(tidyr)
library(gt)

mt <- tibble::as_tibble(mtcars, rownames = "model") |>
    mutate(
        cyl = factor(cyl),
        gear = factor(gear),
        am = factor(am, labels = c("Automatic", "Manual")),
        hp_band = cut(
            hp,
            breaks = c(-Inf, 110, 180, Inf),
            labels = c("Low", "Mid", "High")
        )
    )

summary_tbl <- mt |>
    group_by(cyl, am) |>
    summarise(
        avg_mpg = mean(mpg),
        avg_hp  = mean(hp),
        avg_wt  = mean(wt),
        n       = dplyr::n(),
        .groups = "drop"
    )
```

This document showcases `chanwer` theme functions for `ggplot2` and `gt`,
aligned with chanwe-typst design tokens: Satoshi body, Archivo headings,
primary orange `#FB3D0E`, and the four-color editorial chart palette.

# KPI Summary

:::: {.kpi-grid cols="4"}
::: {.kpi title="VEHICLES" main="32" secondary="mtcars dataset" direction="none"}
:::
::: {.kpi title="AVG MPG" main="20.1" secondary="across all cylinders" direction="none"}
:::
::: {.kpi title="AVG HP" main="146.7" secondary="horsepower" direction="none"}
:::
::: {.kpi title="TRANSMISSION" main="59" unit="%" secondary="automatic" direction="none"}
:::
::::

# GGPlot: Simple

```{r}
#| label: fig-simple-scatter-beige
#| fig-cap: "Scatter — fuel economy vs weight (neutral-100 background)."
#| fig-width: 7
#| fig-height: 4.2

ggplot(mt, aes(wt, mpg, color = am)) +
    geom_point(size = 2.8, alpha = 0.9) +
    scale_color_chanwe_d() +
    theme_chanwe(background = "beige") +
    labs(
        title    = chanwe_title("Fuel economy vs weight"),
        subtitle = chanwe_subtitle("Simple scatter · beige background"),
        x        = "Weight (1000 lbs)",
        y        = "Miles per gallon",
        color    = "Transmission",
        caption  = "Source: Motor Trend, 1974"
    )
```

```{r}
#| label: fig-simple-bar-white
#| fig-cap: "Bar chart — vehicle count by cylinder (white background)."
#| fig-width: 7
#| fig-height: 4.2

ggplot(mt, aes(cyl, fill = cyl)) +
    geom_bar(width = 0.65) +
    scale_fill_chanwe_d() +
    theme_chanwe(background = "white") +
    labs(
        title    = chanwe_title("Vehicle count by cylinder"),
        subtitle = chanwe_subtitle("Simple bar · white background"),
        x        = "Cylinders",
        y        = "Count",
        fill     = "Cylinders"
    )
```

# GGPlot: Complex

```{r}
#| label: fig-complex-facet
#| fig-cap: "Faceted scatter with regression lines."
#| fig-width: 7.4
#| fig-height: 4.8

ggplot(mt, aes(wt, mpg, color = hp_band)) +
    geom_point(size = 2.2, alpha = 0.88) +
    geom_smooth(method = "lm", se = FALSE, linewidth = 0.7) +
    facet_wrap(~am) +
    scale_color_chanwe_d() +
    theme_chanwe(background = "beige") +
    labs(
        title    = chanwe_title("Performance profile by transmission"),
        subtitle = chanwe_subtitle("Faceted by transmission type"),
        x        = "Weight (1000 lbs)",
        y        = "Miles per gallon",
        color    = "HP band"
    )
```

::: {.inset-great-figure eyebrow="DISTRIBUTION" title="Fuel efficiency by cylinder and transmission" layout="left" position="right" color="dark" source="Source: Motor Trend, 1974"}

Vehicles with 4 cylinders show the widest spread and highest median efficiency.
8-cylinder vehicles cluster at lower MPG regardless of transmission type.

```{r}
#| echo: false
#| dev: ragg_png
#| dev.args: !expr list(background = "transparent")
#| fig-width: 5.5
#| fig-height: 4.2

ggplot(mt, aes(cyl, mpg, fill = am)) +
    geom_boxplot(alpha = 0.75, outlier.shape = NA, width = 0.62) +
    geom_jitter(width = 0.12, size = 1.8, alpha = 0.65,
                color = "#FFFFFF") +
    scale_fill_chanwe_d() +
    theme_chanwe(background = "white") +
    theme(
        plot.background  = ggplot2::element_rect(fill = "transparent", color = NA),
        panel.background = ggplot2::element_rect(fill = "transparent", color = NA),
        legend.background = ggplot2::element_rect(fill = "transparent", color = NA),
        legend.key = ggplot2::element_rect(fill = "transparent", color = NA),
        text = ggplot2::element_text(color = "#FFFFFF"),
        axis.text = ggplot2::element_text(color = "#FFFFFF"),
        axis.title = ggplot2::element_text(color = "#FFFFFF"),
        strip.text = ggplot2::element_text(color = "#FFFFFF"),
        legend.title = ggplot2::element_text(color = "#FFFFFF"),
        legend.text = ggplot2::element_text(color = "#FFFFFF")
    ) +
    labs(x = "Cylinders", y = "MPG", fill = "Transmission")
```
:::

# GT Tables: Simple

```{r}
#| label: tbl-simple
#| tbl-cap: "Fleet overview — top 8 vehicles (white background)."

mt |>
    select(model, mpg, cyl, hp, wt) |>
    slice_head(n = 8) |>
    gt(rowname_col = "model") |>
    gt::fmt_number(columns = c(mpg, hp, wt), decimals = 2) |>
    gt::tab_header(
        title    = "Simple fleet view",
        subtitle = "White background"
    ) |>
    gt_theme_chanwe(background = "white")
```

# GT Tables: Compact

```{r}
#| label: tbl-compact
#| tbl-cap: "Fleet overview — compact density (neutral-100 background)."

mt |>
    select(model, mpg, cyl, gear, am) |>
    slice_head(n = 10) |>
    gt(rowname_col = "model") |>
    gt::tab_header(
        title    = "Compact fleet view",
        subtitle = "Neutral-100 background"
    ) |>
    gt_theme_chanwe_compact(background = "beige")
```

# GT Tables: Complex

```{r}
#| label: tbl-complex
#| tbl-cap: "Performance summary — grouped by transmission, with spanners."

summary_tbl |>
    gt(groupname_col = "am") |>
    gt::tab_header(
        title    = "Complex performance summary",
        subtitle = "Grouped by transmission"
    ) |>
    gt::tab_spanner(label = "Averages", columns = c(avg_mpg, avg_hp, avg_wt)) |>
    gt::cols_label(
        cyl     = "Cyl",
        avg_mpg = "MPG",
        avg_hp  = "HP",
        avg_wt  = "Weight",
        n       = "Rows"
    ) |>
    gt::fmt_number(columns = c(avg_mpg, avg_hp, avg_wt), decimals = 2) |>
    gt::fmt_number(columns = n, decimals = 0) |>
    gt::tab_source_note("Source: mtcars aggregated in setup chunk") |>
    gt_theme_chanwe(variant = "spacious", background = "white")
```

# GT Tables: All Variants

```{r}
#| label: tbl-spacious-beige
#| tbl-cap: "Spacious + neutral-100."

summary_tbl |>
    gt(groupname_col = "am") |>
    gt::tab_header(title = "Spacious + Neutral-100") |>
    gt::fmt_number(columns = c(avg_mpg, avg_hp, avg_wt), decimals = 2) |>
    gt_theme_chanwe(variant = "spacious", background = "beige")
```

```{r}
#| label: tbl-spacious-white
#| tbl-cap: "Spacious + white."

summary_tbl |>
    gt(groupname_col = "am") |>
    gt::tab_header(title = "Spacious + White") |>
    gt::fmt_number(columns = c(avg_mpg, avg_hp, avg_wt), decimals = 2) |>
    gt_theme_chanwe(variant = "spacious", background = "white")
```

```{r}
#| label: tbl-compact-beige
#| tbl-cap: "Compact + neutral-100."

summary_tbl |>
    gt(groupname_col = "am") |>
    gt::tab_header(title = "Compact + Neutral-100") |>
    gt::fmt_number(columns = c(avg_mpg, avg_hp, avg_wt), decimals = 2) |>
    gt_theme_chanwe(variant = "compact", background = "beige")
```

```{r}
#| label: tbl-compact-white
#| tbl-cap: "Compact + white."

summary_tbl |>
    gt(groupname_col = "am") |>
    gt::tab_header(title = "Compact + White") |>
    gt::fmt_number(columns = c(avg_mpg, avg_hp, avg_wt), decimals = 2) |>
    gt_theme_chanwe(variant = "compact", background = "white")
```
