---
title: "ChanWe Typst Static Showcase"
subtitle: "Branded non-interactive report template"
author: "Alejandro Abraham"
date: today
topic: "Brand System"
subject: "Typst Static Report"
keywords: [Quarto, Chanwe, Typst, Static, ggplot2]
bibliography: references.bib
link-citations: true
brand: _extensions/chanwe-brand/brand.yml
format:
  typst:
    toc: true
    number-sections: true
execute:
  echo: false
  warning: false
  message: false
---

```{r}
#| label: setup
#| include: false
if (!requireNamespace("chanwer", quietly = TRUE)) {
  devtools::load_all(".")
}

library(chanwer)
library(ggplot2)
library(dplyr)
library(knitr)

mt <- tibble::as_tibble(mtcars, rownames = "model") |>
  mutate(
    cyl = factor(cyl),
    gear = factor(gear),
    am = factor(am, labels = c("Automatic", "Manual"))
  )

summary_tbl <- mt |>
  group_by(cyl) |>
  summarise(
    mpg = mean(mpg),
    hp = mean(hp),
    wt = mean(wt),
    .groups = "drop"
  )
```

This example is optimized for **Typst/PDF output** with no interactive widgets,
so it is stable for sharing and print workflows. It preserves the ChanWe
brand semantics and typography while using static components only
[@allaire2022quarto; @wickham2016ggplot2].

## Executive Notes

::: {.callout-note title="Scope"}
Use this template for board reports, model documentation, and policy notes
where deterministic rendering matters.
:::

::: {.callout-warning title="Compatibility"}
Interactive HTML widgets are intentionally excluded in this Typst template.
:::

## Static Visuals

```{r}
#| label: fig-mpg-vs-weight
#| fig-cap: "Fuel economy versus weight by transmission type."
#| fig-width: 7
#| fig-height: 4.4

ggplot(mt, aes(wt, mpg, color = am)) +
  geom_point(size = 2.6, alpha = 0.9) +
  geom_smooth(method = "lm", se = FALSE, linewidth = 0.8) +
  scale_color_chanwe_d() +
  theme_chanwe() +
  labs(
    title = "Fuel economy profile",
    subtitle = chanwe_subtitle("Static model diagnostic view"),
    x = "Weight",
    y = "MPG",
    color = "Transmission"
  )
```

```{r}
#| label: fig-cylinder-count
#| fig-cap: "Vehicle count by cylinder class."
#| fig-width: 7
#| fig-height: 4.1

ggplot(mt, aes(cyl, fill = cyl)) +
  geom_bar(width = 0.65) +
  scale_fill_chanwe_d() +
  theme_chanwe() +
  labs(
    title = "Fleet composition",
    subtitle = chanwe_subtitle("Distribution by cylinders"),
    x = "Cylinders",
    y = "Count",
    fill = "Cylinders"
  )
```

Figure @fig-mpg-vs-weight and Figure @fig-cylinder-count provide two static
views of the same dataset, suitable for PDF distribution.

## Static Tables

```{r}
#| label: tbl-summary
#| tbl-cap: "Average performance metrics by cylinder group."

kable(summary_tbl, digits = 2, align = c("l", "r", "r", "r"))
```

The semantic token mapping can be presented as a regular static table:

```{r}
#| label: tbl-tokens
#| tbl-cap: "Core semantic color tokens used by the ChanWe brand."

token_tbl <- tibble::tribble(
  ~token, ~value, ~usage,
  "foreground", "#5B5B5B", "Body text",
  "background", "#F7F7F7", "Page surface",
  "primary", "#E94B2B", "Accent/highlight",
  "info", "#11F7E6", "Informational notes",
  "success", "#1EB508", "Positive state",
  "danger", "#F40C0C", "Risk emphasis"
)

kable(token_tbl, align = c("l", "l", "l"))
```

## Equation And Footnote

A simple weighted quality score:

$$
Q = 0.6 \times R + 0.4 \times B
$$ {#eq-quality}

Equation @eq-quality is included as a static mathematical block.^[Use footnotes
for implementation details that should not interrupt the main narrative.]

## References

Citations are rendered in a static bibliography for print-safe output.
